\documentclass[12pt,a4paper]{ltjsreport}
\usepackage{graphicx}
\usepackage{fontspec}
\usepackage{url}
\usepackage{colortbl,array,xcolor}
\usepackage{here}
\usepackage{amsmath}
\usepackage{lmodern}
\usepackage{silence}
\WarningFilter{caption}{Unknown document class (or package)}
\usepackage{subcaption}

\begin{document}
\thispagestyle{empty}
\begin{center}                                                        
コードの時系列変化を考慮した\\
保守性低下の要因分析と改善
\vfill
\vfill
2410064 笹川 尋翔\\
\vfill
主指導教員  鈴木 正人\\
\vfill
北陸先端科学技術大学院大学\\
先端科学技術研究科\\
情報科学\\ 
\vfill
令和8年3月\\ % 学位授与年月
\vfill
\end{center}

% 目次の出力
\tableofcontents

\clearpage
\centerline{概要}
\input{0_overview.tex}
\clearpage

\chapter{はじめに}
\section{背景}
\input{1_1_background.tex}
\section{目的}
\input{1_2_objectives.tex}
\section{構成}
\input{1_3_composition.tex}
\clearpage

\chapter{コード品質と関連研究}
\section{欠陥予測の研究動向}
\input{2_1_research_trends_in_defect_prediction.tex}
\section{構造的メトリクスに基づく欠陥予測}
\input{2_2_defect_prediction_based_on_static_metrics.tex}
\section{変更メトリクスに基づく欠陥予測}
\input{2_3_defect_prediction_based_on_change_metrics.tex}
\section{機械学習を用いた欠陥予測}
\input{2_4_defect_prediction_using_machine_learning.tex}
\section{レビュー効率化とコスト分析}
\input{2_5_review_efficiency_and_cost_analysis.tex}
\clearpage

\chapter{時系列データに基づく分析手法}
\section{コミットの不規則性を考慮した時系列情報の活用}
\input{3_1_research_approach.tex}
\section{構成要素ごとの変更特性の分析}
\input{3_2_change_metrics.tex}
\section{欠陥の特徴の学習とモデル評価}
\input{3_3_machine_learning_model.tex}
\section{レビュー労力を考慮した欠陥予測の改善}
\input{3_4_review_effort_method.tex}
\clearpage

\chapter{実験環境}
\section{汎用性検証のための対象選定}
\input{4_1_dataset_and_projects.tex}
\section{コミット間変化の機械学習可能な形式への変換}
\input{4_2_change_metrics_implementation.tex}
\section{提案手法の効果を検証する比較モデルの準備}
\input{4_3_ml_model_construction.tex}
\section{労力制約下での評価指標の設計}
\input{4_4_review_effort_calculation.tex}
\clearpage

\chapter{実験結果}
\section{段階的評価による各要素の寄与度検証}
\input{5_1_evaluation_methods.tex}
\section{提案手法による予測性能の向上}
\input{5_2_predictive_performance.tex}
\section{提案したメトリクスの高い予測寄与度の確認}
\input{5_3_feature_contribution.tex}
\section{提案メトリクスの分布特性と予測への示唆}
\input{5_4_feature_distribution.tex}
\section{特徴量と予測確率の関係性の解明}
\input{5_5_partial_dependence_plot.tex}
\section{直感的に理解可能な欠陥予測基準の抽出}
\input{5_6_decision_tree_analysis.tex}
\section{同一労力での欠陥発見数増加の実証}
\input{5_7_review_effort_reduction_effect.tex}
\clearpage

\chapter{考察}
\section{観察された現象}
\input{6_1_observed_phenomena_and_questions.tex}
\section{変更規模と欠陥混入確率の関係}
\input{6_2_change_size_and_defect_probability.tex}
\section{プロジェクト間の特徴量重要度の違い}
\input{6_3_feature_importance_variation.tex}
\section{プロジェクト間の予測性能の違い}
\input{6_4_prediction_performance_variation.tex}
\section{研究の制約と妥当性}
\input{6_5_limitations_and_validity.tex}
\clearpage

\chapter{おわりに}
\input{7_conclusion.tex}


\renewcommand{\bibname}{参考文献}
\begin{thebibliography}{99}
\bibitem{kim2014}
Miryung Kim, Thomas Zimmermann, and Nachiappan Nagappan,
``An Empirical Study of Refactoring Challenges and Benefits at Microsoft,''
\textit{IEEE Transactions on Software Engineering},
vol. 40, no. 7, pp. 633--649, July 2014.

\bibitem{kamei2013}
Yasutaka Kamei, Emad Shihab, Bram Adams, Ahmed E. Hassan, Audris Mockus, and Anand Sinha,
``A Large-Scale Empirical Study of Just-in-Time Quality Assurance,''
\textit{IEEE Transactions on Software Engineering},
vol. 39, no. 6, pp. 757--773, June 2013.

\bibitem{ferenc2020}
Rudolf Ferenc, P\'{e}ter Gyimesi, G\'{a}bor Gyimesi, Zolt\'{a}n T\'{o}th, and Tibor Gyim\'{o}thy,
``An Automatically Created Novel Bug Dataset and Its Validation in Bug Prediction,''
\textit{Journal of Systems and Software},
vol. 169, p. 110691, November 2020.

\bibitem{mccabe1976}
Thomas J. McCabe,
``A Complexity Measure,''
\textit{IEEE Transactions on Software Engineering},
Vol. SE-2, No. 4, pp. 308--320, December 1976.

\bibitem{chidamber1994}
Shyam R. Chidamber and Chris F. Kemerer,
``A Metrics Suite for Object Oriented Design,''
\textit{IEEE Transactions on Software Engineering},
Vol. 20, No. 6, pp. 476--493, June 1994.

\bibitem{sliwerski2005}
Jacek \'Sliwerski, Thomas Zimmermann, and Andreas Zeller,
``When Do Changes Induce Fixes?''
\textit{Proc. 2005 International Workshop on Mining Software Repositories (MSR)},
pp. 1--5, May 2005.

\bibitem{jisx0161}
日本産業標準調査会，
``JIS X 0161: 2008 ソフトウェア技術−ソフトウェアライフサイクルプロセス−保守,''
日本規格協会，2008年.

\bibitem{hindle2008}
Abram Hindle, Daniel M. German, and Ric Holt,
``What do large commits tell us? a taxonomical study of large commits,''
\textit{Proc. 2008 International Working Conference on Mining Software Repositories (MSR)},
pp. 99--108, May 2008.

\bibitem{bosu2015}
Amiangshu Bosu, Michaela Greiler, and Christian Bird,
``Characteristics of useful code reviews: an empirical study at microsoft,''
\textit{Proc. 2015 IEEE/ACM 12th Working Conference on Mining Software Repositories (MSR)},
pp. 146--156, 2015.

\bibitem{kononenko2016}
Oleksii Kononenko, Olga Baysal, and Michael W. Godfrey,
``Code review quality: how developers see it,''
\textit{Proc. 38th International Conference on Software Engineering (ICSE)},
pp. 1028--1038, 2016.

\bibitem{ju2021}
An Ju, Hitesh Sajnani, Scot Kelly, and Kim Herzig,
``A Case Study of Onboarding in Software Teams: Tasks and Strategies,''
\textit{Proc. 43rd International Conference on Software Engineering (ICSE)},
pp. 613--623, 2021.

\bibitem{herbold2022}
S. Herbold, A. Trautsch, F. Trautsch, et al.,
``Problems with SZZ and features: An empirical study of the state of practice of defect prediction data collection,''
\textit{Empirical Software Engineering}, vol. 27, article 42, 2022.

\bibitem{just2014}
René Just, Darioush Jalali, and Michael D. Ernst,
``Defects4J: a database of existing faults to enable controlled testing studies for Java programs,''
\textit{Proc. 2014 International Symposium on Software Testing and Analysis (ISSTA)},
pp. 437--440, 2014.

\bibitem{elasticsearch}
Elasticsearch,
``elastic/elasticsearch: Free and Open Source, Distributed, RESTful Search Engine,''
\url{https://github.com/elastic/elasticsearch},
(2025-12-28 参照).

\bibitem{hazelcast}
Hazelcast,
``hazelcast/hazelcast: Hazelcast is a unified real-time data platform combining stream processing with a fast data store, allowing customers to act instantly on data-in-motion for real-time insights.,''
\url{https://github.com/hazelcast/hazelcast},
(2025-12-28 参照).

\bibitem{netty}
The Netty Project,
``netty/netty: Netty project - an event-driven asynchronous network application framework,''
\url{https://github.com/netty/netty},
(2025-12-28 参照).

\bibitem{orientdb}
OrientDB,
``orientechnologies/orientdb: OrientDB is the most versatile DBMS supporting Graph, Document, Reactive, Full-Text and Geospatial models in one Multi-Model product. OrientDB can run distributed (Multi-Master), supports SQL, ACID Transactions, Full-Text indexing and Reactive Queries.,''
\url{https://github.com/orientechnologies/orientdb},
(2025-12-28 参照).

\bibitem{neo4j}
Neo4j,
``neo4j/neo4j: Graphs for Everyone,''
\url{https://github.com/neo4j/neo4j},
(2025-12-28 参照).

\bibitem{hassan2009}
Ahmed E. Hassan,
``Predicting faults using the complexity of code changes,''
\textit{Proc. 2009 IEEE 31st International Conference on Software Engineering (ICSE)},
pp. 78--88, 2009.

\bibitem{fenton1999}
Norman E. Fenton and Martin Neil,
``Software metrics: successes, failures and new directions,''
\textit{Journal of Systems and Software},
vol. 47, no. 2, pp. 149--157, 1999.

\bibitem{graves2000}
T. L. Graves, A. F. Karr, J. S. Marron, and H. Siy,
``Predicting fault incidence using software change history,''
\textit{IEEE Transactions on Software Engineering},
vol. 26, no. 7, pp. 653--661, 2000.

\bibitem{nagappan2005}
Nachiappan Nagappan and Thomas Ball,
``Use of relative code churn measures to predict system defect density,''
\textit{Proc. 27th International Conference on Software Engineering (ICSE)},
pp. 284--292, 2005.

\bibitem{menzies2007}
Tim Menzies, Jeremy Greenwald, and Art Frank,
``Data Mining Static Code Attributes to Learn Defect Predictors,''
\textit{IEEE Transactions on Software Engineering},
vol. 33, no. 1, pp. 2--13, 2007.

\bibitem{ghotra2015}
Baljinder Ghotra, Shane McIntosh, and Ahmed E. Hassan,
``Revisiting the Impact of Classification Techniques on the Performance of Defect Prediction Models,''
\textit{Proc. 2015 IEEE/ACM 37th IEEE International Conference on Software Engineering (ICSE)},
vol. 1, pp. 789--800, 2015.

\bibitem{friedman2001}
Jerome H. Friedman,
``Greedy Function Approximation: A Gradient Boosting Machine,''
\textit{The Annals of Statistics},
vol. 29, no. 5, pp. 1189--1232, 2001.

\bibitem{ostrand2005}
T. J. Ostrand, E. J. Weyuker, and R. M. Bell,
``Predicting the location and number of faults in large software systems,''
\textit{IEEE Transactions on Software Engineering},
vol. 31, no. 4, pp. 340--355, 2005.

\bibitem{mende2010}
Thilo Mende and Rainer Koschke,
``Effort-Aware Defect Prediction Models,''
\textit{Proc. 14th European Conference on Software Maintenance and Reengineering (CSMR)},
pp. 107--116, 2010.

\bibitem{github}
GitHub, Inc.,
``GitHub,''
\url{https://github.com},
(2026-01-02 参照).

\bibitem{replication_package}
笹川 尋翔,
``nagutabby/bug-hunter,''
\url{https://github.com/nagutabby/bug-hunter},
(2026-01-04 参照).

\end{thebibliography}
\end{document}
